Studies of quantum dots

### 2016-11-25 Manuscript/paper.tex
spEnergiesQD: clarify White generator denominators

\subsubsection{White's generator}
\label{subsec:White}

Apart from Wegner's choice of the generator, there exist several other ones in literature. One choice, proposed by White \cite{White:cond-mat0201346}, makes numerical approaches much more efficient.  The problem with Wegner's generator is the widely varying decaying speeds of the Hamiltonian matrix elements.  Terms with large energy separations from the ground state are suppressed initially, followed by those with smaller energy separations.  This leads to stiffness in the flow equation, leading to numerical difficulties in solving the set of coupled differential equations.

@@

The generator is explicitly constructed the following way \cite{PhysRevLett.106.222502,White:cond-mat0201346}
\begin{align}
\hat{\eta}^{\text{Wh}} &\equiv \hat{\eta}' - \hat{\eta}'{}^\dagger
\end{align}
where
\begin{align}
\eta^{\prime [1]}_{a, i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a, i}}{H^{[1]}_{a, a} - H^{[1]}_{i, i} - H^{[2]}_{a, i, a, i}}
\label{eq:WhiteFull1} \\
\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{H^{[1]}_{a, a} + H^{[1]}_{b, b} - H^{[1]}_{i, i} - H^{[1]}_{j, j} + X_{a, b, i, j}}
\label{eq:WhiteFull2} \\
X_{a, b, i, j}
  &\equiv H^{[2]}_{a, b, a, b} - H^{[2]}_{a, i, a, i} - H^{[2]}_{b, i, b, i} \notag \\
  &\qquad + H^{[2]}_{i, j, i, j} - H^{[2]}_{a, j, a, j} - H^{[2]}_{b, j, b, j}
\label{eq:White7}
\end{align}

Compared to Wegner's canonical generator, where the derivative of the final flow equations contain cubes of the Hamiltonian matrix elements (i.e.\ each term contains a product of 3 one-body and/or two-body matrix elements), the elements in White's generator contribute only linearly with White's generator.  This has reduces the stiffness in the differential equation, providing a net increase in computational efficiency since stiff ODE solvers tend to be slower and require more memory.

@@

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=6$ and $\omega=1.0$ ]{
            \label{fig:N6hw1}
            \includegraphics[width=0.38\textwidth]{figures/6parthw1.pdf}
        }
        \subfigure[Results for $N=6$ and $\omega=0.5$ ]{
           \label{fig:N6hw05}
           \includegraphics[width=0.38\textwidth]{figures/6parthw05.pdf}
        }\\ %  ------- End of the first row ----------------------%
        \subfigure[Results for $N=6$ and $\omega=0.28$ ]{
            \label{fig:N6hw028}
            \includegraphics[width=0.38\textwidth]{figures/6parthw028.pdf}
        }
        \subfigure[Results for $N=6$ and $\omega=0.1$ ]{
            \label{fig:N6hw01}
            \includegraphics[width=0.38\textwidth]{figures/6parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=6$ and $\omega=1.0$
       The results are compared with diffusion Monte Carlo (DMC),
      coupled cluster at the level of singles and doubles (CCSD), full
      configuration interaction (FCI) and Hartree-Fock calculations
      (HF) as functions of the number of major oscillator shells
      $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and White's generator. All
      energies in atomic units.}
   \label{fig:N6}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=12$ and $\omega=1.0$ ]{
            \label{fig:N12hw1}
            \includegraphics[width=0.38\textwidth]{figures/12parthw1.pdf}
        }
        \subfigure[Results for $N=12$ and $\omega=0.5$ ]{
           \label{fig:N12hw05}
           \includegraphics[width=0.38\textwidth]{figures/12parthw05.pdf}
        }\\ %  ------- End of the first row ----------------------%
        \subfigure[Results for $N=12$ and $\omega=0.28$ ]{
            \label{fig:N12hw028}
            \includegraphics[width=0.38\textwidth]{figures/12parthw028.pdf}
        }
        \subfigure[Results for $N=12$ and $\omega=0.1$ ]{
            \label{fig:N12hw01}
            \includegraphics[width=0.38\textwidth]{figures/12parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=12$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and White's generator. All
      energies in atomic units.}
   \label{fig:N12}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=20$ and $\omega=1.0$ ]{
            \label{fig:N20hw1}
            \includegraphics[width=0.38\textwidth]{figures/20parthw1.pdf}
        } \subfigure[Results for $N=20$ and $\omega=0.5$ ]{
           \label{fig:N20hw05}
           \includegraphics[width=0.38\textwidth]{figures/20parthw05.pdf}
        }\\ % ------- End of the first row ----------------------%
        \subfigure[Results for $N=20$ and $\omega=0.28$ ]{
            \label{fig:N20hw028}
            \includegraphics[width=0.38\textwidth]{figures/20parthw028.pdf}
        } \subfigure[Results for $N=20$ and $\omega=0.1$ ]{
            \label{fig:N20hw01}
            \includegraphics[width=0.38\textwidth]{figures/20parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=20$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and White's generator. All
      energies in atomic units.}
   \label{fig:N20}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=30$ and $\omega=1.0$ ]{
            \label{fig:N30hw1}
            \includegraphics[width=0.38\textwidth]{figures/30parthw1.pdf}
        } \subfigure[Results for $N=30$ and $\omega=0.5$ ]{
           \label{fig:N30hw05}
           \includegraphics[width=0.38\textwidth]{figures/30parthw05.pdf}
        }\\ % ------- End of the first row ----------------------%
        \subfigure[Results for $N=30$ and $\omega=0.28$ ]{
            \label{fig:N30hw028}
            \includegraphics[width=0.38\textwidth]{figures/30parthw028.pdf}
        } \subfigure[Results for $N=30$ and $\omega=0.1$ ]{
            \label{fig:N30hw01}
            \includegraphics[width=0.38\textwidth]{figures/30parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=30$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and White's generator. All
      energies in atomic units.}
   \label{fig:N30}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=42$ and $\omega=1.0$ ]{
            \label{fig:N42hw1}
            \includegraphics[width=0.38\textwidth]{figures/42parthw1.pdf}
        } \subfigure[Results for $N=42$ and $\omega=0.5$ ]{
           \label{fig:N42hw05}
           \includegraphics[width=0.38\textwidth]{figures/42parthw05.pdf}
        }\\ % ------- End of the first row ----------------------%
        \subfigure[Results for $N=42$ and $\omega=0.28$ ]{
            \label{fig:N42hw028}
            \includegraphics[width=0.38\textwidth]{figures/42parthw028.pdf}
        } \subfigure[Results for $N=42$ and $\omega=0.1$ ]{
            \label{fig:N42hw01}
            \includegraphics[width=0.38\textwidth]{figures/42parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=42$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and White's generator. All
      energies in atomic units.}
   \label{fig:N42}
\end{figure}

\begin{table}
\begin{center}
\caption{Ground state energy (in atomic units) of a circular quantum
  dot, with $N$ particles and oscillator frequency $\omega$. The
  IM-SRG(2) results are given for $R=20$ shells (except for the $N=56$
  results which are for $R=18$), employing a Hartree-Fock basis, a
  bare Coulomb interaction and White's generator. For $N=42$ and
  $\omega=0.1$ results are presented up to $R=22$ major shells. The
  results labelled IM-SRG(2)$_{R\rightarrow \infty}$ are obtained
  using the extrapolation formula of [[equation?]].}
\label{tab:SRGDMC-R20}
\begin{tabular}{ccccc}
\hline\hline
$N$ & $\omega$ & IM-SRG(2) &IM-SRG(2)$_{R\rightarrow \infty}$ & DMC \\
\hline
6 & 1.0 & 20.1583 & 20.1468   & 20.1593(1) \\
& 0.5&11.7690  & 11.7631 &11.7848(1) \\
& 0.28& 7.5713 &   7.5695 &7.6002(1) \\
& 0.1& 3.4962  &  3.4977 &3.5539(1)\\
\hline
12&1.0 & 65.7280 & 65.6990  & 65.7001(1) \\
&0.5 &39.1631 &  39.1473 & 39.1596(1)\\
&  0.28&25.6212 &  25.6140& 25.6358(1)\\
&  0.1&12.2223 &  12.2234 & 12.2698(1)\\
\hline
20& 1.0&155.9737 & 155.9130  & 155.8822(1)\\
&  0.5&93.9219 &   93.8853 &93.8752(1)\\
&  0.28&61.94362 & 61.9240 &61.9268(1) \\
&  0.1&29.95263 &29.9565  & 29.9779(1)\\
\hline
30& 1.0& 308.7673 & 308.6053 & 308.5627(2) \\
 & 0.5& 187.1671& 186.8340 &187.0426(2)\\
 & 0.28&124.0410 & 123.7171 & 123.9683(2) \\
 & 0.1& 60.4319& 60.1158 & 60.4205(2)\\
\hline
42& 1.0&543.3398 & 543.3304 & 542.9428(8) \\
 & 0.5&330.8885 & 330.8425 & 330.6306(2)\\
 & 0.28&220.0226 & 219.9534y &219.8426(2) \\
 & 0.1& 107.7851&  106.8074& 107.6389(2)\\
 \hline
56& 1.0& 880.4159 &  & 879.3986(6) \\
 & 0.5& 538.8199 & & 537.353(2)\\
 & 0.28&360.83689  &  & 358.145(2) \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

In this section, we discuss the IM-SRG results for the ground-state
energies of closed-shell systems. In subsection \ref{subsec:Wegner},
we start with Wegner's canonical generator. Numerical instabilities in
the integration process, as well as a rather slow convergence as
function of the number of oscillator shells, motivate the use of a
Hartree-Fock basis and the Coulomb interaction. Since higher
correlations still lead to stiff equation systems, we change in
subsection \ref{subsec:White} to White's generator. In particular, we
give an overview of the IM-SRG(2) ground state energies for
closed-shell systems up to $N=42$ particles and compare with other
\textit{ab initio} many-body methods.\\ In all our calculations, we
perform the integration of the flow equations using the algorithm
developed by Shampine and Gordon \cite{shampine1975computer}. This
algorithm solves linear systems of differential equations based on the
implicit Adams method, which is a multi-step method of variable
order. Source code is freely available \cite{odesolver}.

@@

We have used IM-SRG to study the ground state energy of circular,
two-dimensional quantum dots up to $N=42$ particles. We utilized two
different generators, Wegner's and White's one, and realized that
Wegner's generator results in stiff equation systems, whereas White's
generator has much better numerics and is computationally more
efficient. Moreover, we found out that the use of an Hartree-Fock
basis improves numerical stability enormously, whereas analogous to
previous FCI \cite{2008arXiv0810.2644K} and CCSD \cite{PhysRevB.84.115302}
calculations, the use of an effective interaction improves convergence
of the ground state energy as function of the number of oscillator
shells.  Our IM-SRG(2) results are in excellent agreement with other
many-body methods, in particular DMC, which can be considered as more
or less exact benchmark. For more than six particles, we lie in all
cases closer to the DMC result than corresponding CCSD calculations
do.

>>>>

\subsubsection{White generator}
\label{subsec:White}

Apart from Wegner's choice of the generator, there exist several other ones in literature. One choice, proposed by White \cite{White:cond-mat0201346}, makes numerical approaches much more efficient.  The problem with the Wegner generator is the widely varying decaying speeds of the Hamiltonian matrix elements.  Terms with large energy separations from the ground state are suppressed initially, followed by those with smaller energy separations.  This leads to stiffness in the flow equation, leading to numerical difficulties in solving the set of coupled differential equations.

@@

The generator is explicitly constructed the following way \cite{PhysRevLett.106.222502,White:cond-mat0201346}
\begin{align*}
\hat{\eta}^{\text{Wh}} &\equiv \hat{\eta}' - \hat{\eta}'{}^\dagger
\end{align*}
where
\begin{align*}
\eta^{\prime [1]}_{a, i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a, i}}{\Delta^{[1]}_{a, i}} &
\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{\Delta^{[2]}_{a, b, i, j}}
\end{align*}
and the denominators $\Delta^{[1]}$ and $\Delta^{[2]}$ are
\begin{align*}
\Delta^{[1]}_{a, i} &\equiv H^{[1]}_{a, a} - H^{[1]}_{i, i} - H^{[2]}_{a, i, a, i} \\
\Delta^{[2]}_{a, b, i, j} &\equiv H^{[1]}_{a, a} + H^{[1]}_{b, b} - H^{[1]}_{i, i} - H^{[1]}_{j, j} + X_{a, b, i, j} \\
X_{a, b, i, j}
  &\equiv H^{[2]}_{a, b, a, b} - H^{[2]}_{a, i, a, i} - H^{[2]}_{b, i, b, i} \notag \\
  &\qquad + H^{[2]}_{i, j, i, j} - H^{[2]}_{a, j, a, j} - H^{[2]}_{b, j, b, j}
\end{align*}
These are the Epstein--Nesbet denominators.  Some literature use M\o eller--Plesset denominators, which omit the $X_{a, b, i, j}$ term, leading to a slightly different variant of the canonical White generator.

Compared to the Wegner generator, where the derivative of the final flow equations contain cubes of the Hamiltonian matrix elements (i.e.\ each term contains a product of 3 one-body and/or two-body matrix elements), the elements in White generators contribute only linearly.  This has reduces the stiffness in the differential equation, providing a net increase in computational efficiency since stiff ODE solvers tend to be slower and require more memory.

@@

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=6$ and $\omega=1.0$ ]{
            \label{fig:N6hw1}
            \includegraphics[width=0.38\textwidth]{figures/6parthw1.pdf}
        }
        \subfigure[Results for $N=6$ and $\omega=0.5$ ]{
           \label{fig:N6hw05}
           \includegraphics[width=0.38\textwidth]{figures/6parthw05.pdf}
        }\\ %  ------- End of the first row ----------------------%
        \subfigure[Results for $N=6$ and $\omega=0.28$ ]{
            \label{fig:N6hw028}
            \includegraphics[width=0.38\textwidth]{figures/6parthw028.pdf}
        }
        \subfigure[Results for $N=6$ and $\omega=0.1$ ]{
            \label{fig:N6hw01}
            \includegraphics[width=0.38\textwidth]{figures/6parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=6$ and $\omega=1.0$
       The results are compared with diffusion Monte Carlo (DMC),
      coupled cluster at the level of singles and doubles (CCSD), full
      configuration interaction (FCI) and Hartree-Fock calculations
      (HF) as functions of the number of major oscillator shells
      $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and the White generator. All
      energies in atomic units.}
   \label{fig:N6}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=12$ and $\omega=1.0$ ]{
            \label{fig:N12hw1}
            \includegraphics[width=0.38\textwidth]{figures/12parthw1.pdf}
        }
        \subfigure[Results for $N=12$ and $\omega=0.5$ ]{
           \label{fig:N12hw05}
           \includegraphics[width=0.38\textwidth]{figures/12parthw05.pdf}
        }\\ %  ------- End of the first row ----------------------%
        \subfigure[Results for $N=12$ and $\omega=0.28$ ]{
            \label{fig:N12hw028}
            \includegraphics[width=0.38\textwidth]{figures/12parthw028.pdf}
        }
        \subfigure[Results for $N=12$ and $\omega=0.1$ ]{
            \label{fig:N12hw01}
            \includegraphics[width=0.38\textwidth]{figures/12parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=12$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and the White generator. All
      energies in atomic units.}
   \label{fig:N12}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=20$ and $\omega=1.0$ ]{
            \label{fig:N20hw1}
            \includegraphics[width=0.38\textwidth]{figures/20parthw1.pdf}
        } \subfigure[Results for $N=20$ and $\omega=0.5$ ]{
           \label{fig:N20hw05}
           \includegraphics[width=0.38\textwidth]{figures/20parthw05.pdf}
        }\\ % ------- End of the first row ----------------------%
        \subfigure[Results for $N=20$ and $\omega=0.28$ ]{
            \label{fig:N20hw028}
            \includegraphics[width=0.38\textwidth]{figures/20parthw028.pdf}
        } \subfigure[Results for $N=20$ and $\omega=0.1$ ]{
            \label{fig:N20hw01}
            \includegraphics[width=0.38\textwidth]{figures/20parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=20$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and the White generator. All
      energies in atomic units.}
   \label{fig:N20}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=30$ and $\omega=1.0$ ]{
            \label{fig:N30hw1}
            \includegraphics[width=0.38\textwidth]{figures/30parthw1.pdf}
        } \subfigure[Results for $N=30$ and $\omega=0.5$ ]{
           \label{fig:N30hw05}
           \includegraphics[width=0.38\textwidth]{figures/30parthw05.pdf}
        }\\ % ------- End of the first row ----------------------%
        \subfigure[Results for $N=30$ and $\omega=0.28$ ]{
            \label{fig:N30hw028}
            \includegraphics[width=0.38\textwidth]{figures/30parthw028.pdf}
        } \subfigure[Results for $N=30$ and $\omega=0.1$ ]{
            \label{fig:N30hw01}
            \includegraphics[width=0.38\textwidth]{figures/30parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=30$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and the White generator. All
      energies in atomic units.}
   \label{fig:N30}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=42$ and $\omega=1.0$ ]{
            \label{fig:N42hw1}
            \includegraphics[width=0.38\textwidth]{figures/42parthw1.pdf}
        } \subfigure[Results for $N=42$ and $\omega=0.5$ ]{
           \label{fig:N42hw05}
           \includegraphics[width=0.38\textwidth]{figures/42parthw05.pdf}
        }\\ % ------- End of the first row ----------------------%
        \subfigure[Results for $N=42$ and $\omega=0.28$ ]{
            \label{fig:N42hw028}
            \includegraphics[width=0.38\textwidth]{figures/42parthw028.pdf}
        } \subfigure[Results for $N=42$ and $\omega=0.1$ ]{
            \label{fig:N42hw01}
            \includegraphics[width=0.38\textwidth]{figures/42parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=42$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and the White generator. All
      energies in atomic units.}
   \label{fig:N42}
\end{figure}

\begin{table}
\begin{center}
\caption{Ground state energy (in atomic units) of a circular quantum
  dot, with $N$ particles and oscillator frequency $\omega$. The
  IM-SRG(2) results are given for $R=20$ shells (except for the $N=56$
  results which are for $R=18$), employing a Hartree-Fock basis, a
  bare Coulomb interaction and the White generator. For $N=42$ and
  $\omega=0.1$ results are presented up to $R=22$ major shells. The
  results labelled IM-SRG(2)$_{R\rightarrow \infty}$ are obtained
  using the extrapolation formula of [[equation?]].}
\label{tab:SRGDMC-R20}
\begin{tabular}{ccccc}
\hline\hline
$N$ & $\omega$ & IM-SRG(2) &IM-SRG(2)$_{R\rightarrow \infty}$ & DMC \\
\hline
6 & 1.0 & 20.1583 & 20.1468   & 20.1593(1) \\
& 0.5&11.7690  & 11.7631 &11.7848(1) \\
& 0.28& 7.5713 &   7.5695 &7.6002(1) \\
& 0.1& 3.4962  &  3.4977 &3.5539(1)\\
\hline
12&1.0 & 65.7280 & 65.6990  & 65.7001(1) \\
&0.5 &39.1631 &  39.1473 & 39.1596(1)\\
&  0.28&25.6212 &  25.6140& 25.6358(1)\\
&  0.1&12.2223 &  12.2234 & 12.2698(1)\\
\hline
20& 1.0&155.9737 & 155.9130  & 155.8822(1)\\
&  0.5&93.9219 &   93.8853 &93.8752(1)\\
&  0.28&61.94362 & 61.9240 &61.9268(1) \\
&  0.1&29.95263 &29.9565  & 29.9779(1)\\
\hline
30& 1.0& 308.7673 & 308.6053 & 308.5627(2) \\
 & 0.5& 187.1671& 186.8340 &187.0426(2)\\
 & 0.28&124.0410 & 123.7171 & 123.9683(2) \\
 & 0.1& 60.4319& 60.1158 & 60.4205(2)\\
\hline
42& 1.0&543.3398 & 543.3304 & 542.9428(8) \\
 & 0.5&330.8885 & 330.8425 & 330.6306(2)\\
 & 0.28&220.0226 & 219.9534y &219.8426(2) \\
 & 0.1& 107.7851&  106.8074& 107.6389(2)\\
 \hline
56& 1.0& 880.4159 &  & 879.3986(6) \\
 & 0.5& 538.8199 & & 537.353(2)\\
 & 0.28&360.83689  &  & 358.145(2) \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

In this section, we discuss the IM-SRG results for the ground-state
energies of closed-shell systems. In subsection \ref{subsec:Wegner},
we start with the Wegner generator. Numerical instabilities in
the integration process, as well as a rather slow convergence as
function of the number of oscillator shells, motivate the use of a
Hartree-Fock basis and the Coulomb interaction. Since higher
correlations still lead to stiff equation systems, we change in
subsection \ref{subsec:White} to the White generator. In particular, we
give an overview of the IM-SRG(2) ground state energies for
closed-shell systems up to $N=42$ particles and compare with other
\textit{ab initio} many-body methods.\\ In all our calculations, we
perform the integration of the flow equations using the algorithm
developed by Shampine and Gordon \cite{shampine1975computer}. This
algorithm solves linear systems of differential equations based on the
implicit Adams method, which is a multi-step method of variable
order. Source code is freely available \cite{odesolver}.

@@

We have used IM-SRG to study the ground state energy of circular,
two-dimensional quantum dots up to $N=42$ particles. We utilized two
different generators, Wegner and White generators, and realized that
the Wegner generator results in stiff equation systems, whereas the White
generator has much better numerics and is computationally more
efficient. Moreover, we found out that the use of an Hartree-Fock
basis improves numerical stability enormously, whereas analogous to
previous FCI \cite{2008arXiv0810.2644K} and CCSD \cite{PhysRevB.84.115302}
calculations, the use of an effective interaction improves convergence
of the ground state energy as function of the number of oscillator
shells.  Our IM-SRG(2) results are in excellent agreement with other
many-body methods, in particular DMC, which can be considered as more
or less exact benchmark. For more than six particles, we lie in all
cases closer to the DMC result than corresponding CCSD calculations
do.
